Parametrization of Invertible Resnets up to Homology Equivalence for Abelian Lie Groups

### 2020-04-02 llncs2e/paper77.tex
typos

\begin{proof}
Let $\{K^{\omega_{i}}\}_{i \in I}$ be the set of all connected components of the simplicial complex $K(X)$ of a point set $X$ and $H^{\Delta}_k\left(K\left(X\right)\right)$ its simplicial homology groups. We denote the homology groups of the components with $H_k^{\Delta}(K^{\omega_{i}}(X))$. With $C_k(K^{\omega_{i}}(X))$, we denote the group of $k$-chains for the connected component of the simplicial complex. Then $C_k(K^{\omega_{i}}(X)) \subseteq C_k(K(X))$ is a subgroup for all $i$.

@@

\begin{proof}
Using the boundary operator, which is a homomorphism of groups, we get $C_{k-1}(K(X)) \simeq \bigoplus_{i \in I} \partial_k(C_{k}(K^{\omega_{i}}(X)))$. An element in the $(k+1)$-th chain group $v \in C_{k+1}(K(X))$ is represented by $v = \sum_{i \in I} v_{\omega_{i}}$. Thus $\partial_{k+1}(v) \in C_{k}(K(X))$ can be broken down to $\partial_{k+1}(v) = \sum_{i \in I} \partial_{k+1}(v_{\omega_{i}})$ where $v_{\omega_{i}} \in C^\omega_{k+1}(K^{\omega_{i}})$.\qed
\end{proof}

The groups of coundaries can also be decomposed. The kernel of $C_k(K^{\omega_{i}}(X))$ can be written as $\ker \partial_k(C_k(K^{\omega_{i}}(X)))$ $= \ker \partial_k(C_k(K(X)))$ $\cap$ $C_k(K^{\omega_{i}}(X))$.
\begin{align}
	\ker \partial_k &\simeq \bigoplus_{i \in I} \partial_k\left(C_k\left(K^{\omega_{i}}(X)\right)\right), \text{which implies}\\
	&\Rightarrow \frac{\ker \partial_k\left(C_k\left(K\left(X\right)\right)\right)}{\Ima \partial_{k+1}\left(C_{k+1}\left(K\left(X\right)\right)\right)} \simeq \bigoplus_{i \in I} \frac{\ker \partial_k(C_k(K^{\omega_{i}}(X)))}{\Ima \partial_{k+1}(C_{k+1}(K^{\omega_{i}}(X)))}\\
	&\Rightarrow H^{\Delta}_k(K(X)) \simeq \bigoplus_{i \in I} H^{\Delta}_k(K^{\omega_{i}}(X)).
\end{align}
\qed
\end{proof}

@@

\begin{remarkdef}
Since for simplicial complexes, the property to be connected corresponds to path-connectedness, the coordinatewise sum of the connected components is a generator of the whole group.
\end{remarkdef}

>>>>

\begin{proof}
Let $\{K^{\omega_{i}}\}_{i \in I}$ be the set of all connected components of the simplicial complex $K(X)$ of a point set $X$ and $H^{\Delta}_k\left(K\left(X\right)\right)$ its simplicial homology groups. We denote the homology groups of the components with $H_k^{\Delta}(K^{\omega_{i}}(X))$. With $C_k(K^{\omega_{i}}(X))$, we denote the group of $k$-chains for the connected components of the simplicial complex. Then $C_k(K^{\omega_{i}}(X)) \subseteq C_k(K(X))$ is a subgroup for all $i$.

@@

\begin{proof}
Using the boundary operator, which is a homomorphism of groups, we get $C_{k-1}(K(X)) \simeq \bigoplus_{i \in I} \partial_k(C_{k}(K^{\omega_{i}}(X)))$. An element in the $(k+1)$-th chain group $v \in C_{k+1}(K(X))$ is represented by $v = \sum_{i \in I} v_{\omega_{i}}$. Thus $\partial_{k+1}(v) \in C_{k}(K(X))$ can be broken down to $\partial_{k+1}(v) = \sum_{i \in I} \partial_{k+1}(v_{\omega_{i}})$ where $v_{\omega_{i}} \in C^\omega_{k+1}(K^{\omega_{i}}(X))$.\qed
\end{proof}

The groups of boundaries can also be decomposed. The kernel of $C_k(K^{\omega_{i}}(X))$ can be written as $\ker \partial_k(C_k(K^{\omega_{i}}(X)))$ $= \ker \partial_k(C_k(K(X)))$ $\cap$ $C_k(K^{\omega_{i}}(X))$.
\begin{align}
	\ker \partial_k &\simeq \bigoplus_{i \in I} \partial_k\left(C_k\left(K^{\omega_{i}}(X)\right)\right), \text{which implies}\\
	&\Rightarrow \frac{\ker \partial_k\left(C_k\left(K\left(X\right)\right)\right)}{\Ima \partial_{k+1}\left(C_{k+1}\left(K\left(X\right)\right)\right)} \simeq \bigoplus_{i \in I} \frac{\ker \partial_k(C_k(K^{\omega_{i}}(X)))}{\Ima \partial_{k+1}(C_{k+1}(K^{\omega_{i}}(X)))}\\
	&\Rightarrow H^{\Delta}_k(K(X)) \simeq \bigoplus_{i \in I} H^{\Delta}_k(K^{\omega_{i}}(X)).
\end{align}
\qed
\end{proof}

@@

\begin{remarkdef}
Since for simplicial complexes the property to be connected corresponds to path-connectedness, the coordinatewise sum of the connected components is a generator of the whole group.
\end{remarkdef}
